\textbf{Computational Fuzzy Extractors}

### 2013-06-20 trunk/CompFuzzExt.tex
Changing claim B.1 to match A.3

\begin{construction}
Let $n$ be a security parameter and let $m\ge n$.  Let $q$ be a prime. %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\decode_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, X\in\Fq^n$ uniformly.
\item Compute $p = (\vA, \vA X+w)$, \\\ $r = X_{1,...,n/2}$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $p$ as $(\vA, \vect{C})$; let $\vect{B}=\vect{C}-w'$.
\item Let $X = \decode_t(\vA, \vect{B})$\\
\item Output $r = X_{1,...,n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

@@

\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}
Let $n$ be a security parameter.  
Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime\footnote{%
Unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding.}.
%
Let $\vA$ be the uniform distribution over  $\Fq^{m\times n}$, $\vx$ be the uniform distribution over $\Fq^n$ and $\chi$ be an arbitrary distribution on $\Fq^m$.
 The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish the distribution
$(\vA, \vA\vx+\chi)$ from
 the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.

@@

\begin{construction}
\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe $\decode_t$:
\begin{enumerate}
\item Input $\vA , \vB = \vA X + W - W'$
\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
\item Restrict $\vA, \vB$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, \vB_{i_1,...,i_{2n}}$.
\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
If no such rows exist, output $\perp$ and stop.
\item Denote by $\vA', \vB'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vB_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $X' = (\vA')^{-1}B'$.  
\item If $\vB- \vA X'$ has more than $t$ nonzero coordinates, go to step (2).
\item Output $X'$.
\end{enumerate}
\end{construction}

Each step is computable in time $O(n^3)$. 
For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $W$ and $W'$ agree on those rows).  If this happens, and $\vA_{i_1,...,i_{2n}}$ has rank  $n$ (which is highly likely), then $X'=X$, and the algorithm terminates.  However, we also need to ensure correctness: we need to make sure that if $X'\neq X$, we detect it in step 6.  This detection will happen if $B-\vA X' = \vA (X-X')+(W-W')$ has more than $t$ nonzero coordinates.  It suffices to ensure that $\vA (X-X')$ has at least $2t+1$ nonzero coordinates (because at most $t$ of those can be zeroed out by $W-W'$), which happens whenever the code generated by $\vA$ has distance $2t+1$.

Setting $t = O(\frac{m}{n}\log n)$ is sufficient to ensure efficiency.    Random linear codes have distance at least $O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$ (the exact statement is in \corref{cor:code high distance}), so this also ensures correctness.
The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\decode_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\decode_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d (m/n-2)\log n$]
\label{lem:i t poly time}
%Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$. 
Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.  Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$~(this probability is over the choice of random coins of \rep).  It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$ and random choices made by $\decode_t$).
\end{lemma}

@@

We also need that random matrices are full rank with high probability~(to allow us to decode).  We use the following claim~(techniques from Cooper~\cite{cooper2000rank}):
\begin{claim}
\label{cl:full rank matrix}
Let $q\ge 2$ be a prime.  Let $\alpha, \beta$ be integers and let 
let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be uniformly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \alpha q^{\beta}$.
\end{claim}
\begin{proof}
The probability that all $\alpha$ rows are linearly independent is the successive probability that each row is linearly independent of the previous rows, for the $i$th row this probability is $q^{i-1}/q^{\alpha+\beta}$.  By union bound and $\beta = \omega(1)$, the probability that $\vS$ is not full rank is:
\begin{align*}
\Pr[\rank(\vS) < \alpha] &= \sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
\leq \alpha \frac{q^{\alpha}}{q^{\alpha+\beta} }= \alpha q^{-\beta}.
\end{align*}
\end{proof}

@@

\begin{figure}[p]
\begin{framed}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vQ \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of these indices.
\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
\subitem For $j=1,..., m$:
\subsubitem Generate $\vQ_{j, i}\overset{\$}\leftarrow \Fq$
\subsubitem Set $b_j^* = b_j^* + \vQ_{j, i} x_i$.
\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vQ\\\hline \vR & \vS\end{array}\right)$.
\item \label{step:randomization}
For {$i=1,..., m$}:
\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1 \times \alpha}$.
\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
\item Run $D$ on input $\vA, \vb$.
\item Output $D$'s output.
\end{enumerate}
\end{framed}
\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
\label{fig:perfectLWEreduction}
\end{figure}
The distinguisher $D'$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability:
\begin{claim}
\label{cl:full rank matrix 5.2}
Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
\end{claim}
\begin{proof}
Direct application of \clref{cl:full rank matrix} when $\alpha = \poly(n)$ and $\beta = \omega(1)$ in $n$.
\end{proof}
\begin{corollary}
$
|\Pr[D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
$
\end{corollary}

@@

\subsection{Proof of \lemref{lem:i t poly time}}
\label{sec:proof lem i t poly time}
\begin{proof}
Note that $\decode_t$ will stop if $W$ and $W'$ agree on all the rows selected in Step 2 (it may also stop for other reasons---namely, in step 4; but we do not use this fact to bound the expected running time).
The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.  That is,
\begin{align*}
\Pr[i_1,..., i_{2n}\text{ have no errors}]&\geq \prod_{i=0}^{2n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\left(\frac{m}{n}-2\right)\log n}{m-i}\right)\\
&\geq  \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-2n}{m-i}\right)\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\right) \\
&= \left(1-\frac{d\log n}{n}\right)^{2n}  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{2d\log n}\geq \frac{1}{4^{2d\log n}} = \frac{1}{n^{4d}}\,.
\end{align*}
(The second-to-last step holds as long as $n\ge 2d\log n$.) Because at each iteration, we select $2n$ rows independently at random, the expected number of iterations is at most $n^{4d}$; each iteration takes $O(n^3)$ operations in $\Fq$, which gives us the expected running time bound.

The probability that $\decode_t$ outputs $\perp$ is bounded by 
\begin{eqnarray*}
\Pr[\decode_t\rightarrow \perp]& \le & \sum_{j=1}^\infty \Pr[\decode_t\rightarrow \perp \text{ in $j$th iteration of step 4}]\\
&= &\sum_{j=1}^\infty  \Pr[\decode_t \text{ has not stopped after $j-1$ iterations} \wedge \rank(\vA_{i_1},\dots, \vA_{i_{2n}})<n]\\
&\le &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times} \wedge \rank(\vA_{i_1},\dots, \vA_{i_{2n}})<n]\\
&\le &\sum_{j=1}^\infty  \left(1-\frac{1}{n^{4d}}\right)^{j-1} \cdot e^{-\Omega(n)}\\
& = & n^{4d} e^{-\Omega(n)} = e^{-\Omega(n)}\,.
\end{eqnarray*}
(the second to last line follows from \clref{cl:full rank matrix} when $\alpha, \beta = O(n)$ \bnote{need to say this is a randomly generated matrix, but there are previous iterations.  I know we abort if we find a non full rank matrix but this still bothers me.}).

We claim that if the code generated by $\vA$ 
has distance at least $2t+1$, then $\decode_t$ will output $\perp$ or the correct $X'=X$.
Indeed, suppose $X'\neq X$. Since $\vA (X-X')$ has at least $2t+1$ nonzero coordinates by the minimum distance of the code generated by $\vA$, and at most  $t$ of those can be zeroed out by the addition of  $W-W'$, such an $X'$ will not pass Step 6.

>>>>

\begin{construction}
Let $n$ be a security parameter and let $m\ge n$.  Let $q$ be a prime. %Let $W = W_1,..., W_m$ and let $b$ be a constant and let $W_i \in \zo^b$ for all $i$.  
Define $\gen, \rep$ as follows:%The following construction is a computational secure sketch:
%Code-offset construction of a secure sketch using a random linear code over a finite field $\Fq$. $\decode_t (\vA, \vect{D})$ denotes an algorithm that decodes up to $t$ errors, i.e., an algorithm that finds $X'\in \Fq^n$ such that $\vect{A}X'$ is of Hamming distance at most $t$ from $\vect{D}$. $m > n$ are parameters to be figured out later.
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w\leftarrow W$ (where $W$ is some distribution over $\Fq^m$).
\item Sample $\vA\in\Fq^{m\times n}, \vx\in\Fq^n$ uniformly.
\item Compute $p = (\vA, \vA \vx+w)$, \\\ $r = \vx_{1,...,n/2}$.
\item Output $(r, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ (where the Hamming distance between $w'$ and $w$ is at most $t$).
\item Parse $p$ as $(\vA, \vect{c})$; let $\vb=\vect{c}-w'$.
\item Let $x = \decode_t(\vA, \vb)$\\
\item Output $r = x_{1,...,n/2}$.
\end{enumerate}
\end{minipage} 
\end{tabular}
\end{center}
\label{cons:informal construction}
\end{construction}

@@

\begin{definition}[Decisional $\lwe$]\label{def:dist-LWE}
Let $n$ be a security parameter.  
Let $m = m(n) = \poly(n)$ be an integer and $q = q(n) = \poly(n)$ be a prime\footnote{%
Unlike in common formulations of LWE, where $q$ can be any integer, we need $q$ to be prime for decoding.}.
%
Let $\vA$ be the uniform distribution over  $\Fq^{m\times n}$, $X$ be the uniform distribution over $\Fq^n$ and $\chi$ be an arbitrary distribution on $\Fq^m$.
 The decisional version of the $\LWE$ problem, denoted \class{dist}-$\LWE_{n, m, q, \chi}$, is to distinguish the distribution
$(\vA, \vA X+\chi)$ from
 the uniform distribution over $(\Fq^{m\times n}, \Fq^m)$.

@@

\begin{construction}
\label{cons:decoding algorithm} We consider a setting of $(n, m, q, \chi)$ where $m\geq 3n$.  We describe $\decode_t$:
\begin{enumerate}
\item Input $\vA , \vb = \vA \vx + w - w'$
\item Randomly select rows without replacement $i_1,..., i_{2n}\leftarrow [1,m]$.  
\item Restrict $\vA, \vb$ to rows $i_1,...,i_{2n}$; denote these $\vA_{i_1,...,i_{2n}}, \vb_{i_1,...,i_{2n}}$.
\item Find $n$ rows of $\vA_{i_1,..., i_{2n}}$ that are linearly independent.  
If no such rows exist, output $\perp$ and stop.
\item Denote by $\vA', \vb'$ the restriction of $\vA_{i_1,..., i_{2n}}, \vb_{i_1,..., i_{2n}}$ (respectively) to these rows. Compute $\vx' = (\vA')^{-1}\vb'$.  
\item If $\vb- \vA \vx'$ has more than $t$ nonzero coordinates, go to step (2).
\item Output $\vx'$.
\end{enumerate}
\end{construction}

Each step is computable in time $O(n^3)$. 
For $\decode_t$ to be efficient, we need $t$ to be small enough so that  with probability at least $\frac{1}{\poly(n)}$, none of the $2n$ rows  selected  in step 2 have errors (i.e., so that $w$ and $w'$ agree on those rows).  If this happens, and $\vA_{i_1,...,i_{2n}}$ has rank  $n$ (which is highly likely), then $\vx'=\vx$, and the algorithm terminates.  However, we also need to ensure correctness: we need to make sure that if $\vx'\neq \vx$, we detect it in step 6.  This detection will happen if $\vb-\vA \vx' = \vA (\vx-\vx')+(w-w')$ has more than $t$ nonzero coordinates.  It suffices to ensure that $\vA (\vx-\vx')$ has at least $2t+1$ nonzero coordinates (because at most $t$ of those can be zeroed out by $w-w'$), which happens whenever the code generated by $\vA$ has distance $2t+1$.

Setting $t = O(\frac{m}{n}\log n)$ is sufficient to ensure efficiency.    Random linear codes have distance at least $O(\frac{m}{n}\log n)$ with probability $1-e^{-\Omega(n)}$ (the exact statement is in \corref{cor:code high distance}), so this also ensures correctness.
The formal statement is below~(proof in \secref{sec:proof lem i t poly time}):
%  We provide the results in \lemref{lem:i t constant time} and \lemref{lem:i t poly time} respectively~(proofs in Sections~\ref{sec:proof lem i t constant time},~\ref{sec:proof lem i t poly time}).  \lnote{can we combine these lemmas into one?  It's hard for the reader to compare line-by-line to see where the differences are.  More errors seems better; we could simply point out that constant number of erros leads to better running time, right in the statement of the lemma or right after it}
%\begin{lemma}[Efficiency of $\decode_t$ when $t\leq m/n-1$]
%\label{lem:i t constant time}
%Let $\vA, \vA X+E$ be a  $(n,m, q, \chi)$-LWE instance that is a unique witness relation~(except with negligible probability).  Assume $d(E, E')\leq t$ where $t \leq (m-n)/n$.  Then $\decode_t$ runs in expected time $O(n^3\log q+ s_{ver})$ on input distribution $\vA, \vA X+E - E'$ and outputs $X' =X$ for all but a negligible fraction of inputs over $\vA, \vA X+E - E'$.
%\end{lemma}
\begin{lemma}[Efficiency of $\decode_t$ when $t\leq d (m/n-2)\log n$]
\label{lem:i t poly time}
%Let $\vA, \vA X+W$ be a  $\distLWE_{n,m, q, \chi}$ instance where $m\geq 3n$.  Assume that $W$ is split into $m$ blocks of length $b$ and let $\dis$ be the Hamming distance over alphabet $2^b$. 
Let $d$ be a positive constant and assume that $\dis(W, W')\leq t$ where $t\leq d(\frac{m}{n}-2)\log n$.  Then $\decode_t$ runs in expected time $O(n^{4d+3})$ operations in $\Fq$~(this expectation is over the choice of random coins of $\decode_t$, regardless of the input, as long as $\dis(w, w')\le t$).  It outputs $X$ with probability $1-e^{-\Omega(n)}$ (this probability is over the choice of the random matrix  $\vA$ and random choices made by $\decode_t$).
\end{lemma}

@@

We also need that random matrices are full rank with high probability~(to allow us to decode).  We use the following claim~(techniques from Cooper~\cite{cooper2000rank}):
\begin{claim}
\label{cl:full rank matrix}
Let $q\ge 2$ be a prime.  Let $\alpha, \beta$ be integers and let 
let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be uniformly generated.  Then $\Pr[\rank(\vS)=\alpha] >  1- q^{-\beta}$.
\end{claim}
\begin{proof}
Let $p_i$ be the probability that the $i$th
row is linearly dependent on the previous $i-1$ rows. 
By the union bound, the probability that $\alpha$ rows are linearly dependent is bounded by 
$\sum_{i=1}^\alpha p_i$.
Since $i-1$ rows can span a space of size at most $q^{i-1}$, the probability $p_i$ that a randomly chosen $i$th row is in that space is at most $q^{i-1}/q^{\alpha+\beta}$. So
\begin{align*}
\Pr[\rank(\vS) < \alpha] &=\sum_{i=1}^{\alpha} \frac{q^{i-1}}{q^{\alpha+\beta}}
= \frac{q^{\alpha}-1}{q-1}\frac{1}{q^{\alpha+\beta} }< q^{-\beta}.
\end{align*}
\end{proof}

@@

\begin{figure}[p]
\begin{framed}
\begin{enumerate}
\item Input $\vA', \vb'$, where $\vA' \overset{\$} \leftarrow \Fq^{m\times n}$ and $\vb'$ is either uniform over $\Fq^m$ or $\vb' = \vA'\vx' +\ve'$.
\item Randomly generate $\vect{R} \overset{\$}\leftarrow \Fq^{\alpha \times n}$. Initialize $\vQ \in \Fq^{n\times (\alpha+\beta)}$ to be the zero matrix.
\item Let $\vb^* = (\vb', b^*_{m+1}, \ldots,b^*_{m+\alpha})$, where $(b^*_{m+1}, \ldots, b^*_{m+\alpha} )\overset{\$} \leftarrow \Fq^\alpha$.\label{step:b generation}
\item Randomly generate $\vect{S} \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$.
		\subitem If $\rank(\vect{S})<\alpha$, stop and output a random bit.
\item Find a set of $\alpha$ linearly independent columns in $\vS$.  Let $T$ be the set of these indices.
\item For all $x_i$ where $n\leq i$ and $i\not \in T$:\label{step:fill in matrix}
\subitem Generate $x_i\overset{\$}\leftarrow \Fq$.  
\subitem For $j=1,..., m$:
\subsubitem Generate $\vQ_{j, i}\overset{\$}\leftarrow \Fq$
\subsubitem Set $b_j^* = b_j^* + \vQ_{j, i} x_i$.
\item Initialize $\vA^*  = \left(\begin{array}{c | c}\vA' & \vQ\\\hline \vR & \vS\end{array}\right)$.
\item \label{step:randomization}
For {$i=1,..., m$}:
\subitem Randomly generate $\gamma_i \leftarrow \Fq^{1 \times \alpha}$.
\subitem Set $\va_{i} \leftarrow \va^*_{i}+\gamma_i (\vR||\vS)$
\subitem Set $b_i \leftarrow b^*_i + \gamma_i (b^*_{m+1},..., b^*_{m+k})$
\item Run $D$ on input $\vA, \vb$.
\item Output $D$'s output.
\end{enumerate}
\end{framed}
\caption{A PPT $D'$ that distinguishes LWE using distinguisher for LWE w/ block fixing source}
\label{fig:perfectLWEreduction}
\end{figure}
The distinguisher $D'$ has an advantage when $S$ is of rank $\alpha$.  This occurs with overwhelming probability:
\begin{claim}
\label{cl:full rank matrix 5.2}
Let $\vS \overset{\$}\leftarrow \Fq^{\alpha \times (\alpha+\beta)}$ be randomly generated.  Then $\Pr[\rank(\vS)=\alpha]\geq  1- \ngl(n)$.
\end{claim}
\begin{proof}
Direct result of \clref{cl:full rank matrix} when $\beta = \omega(1)$ in $n$.
\end{proof}
\begin{corollary}
$
|\Pr[D(\vA, \vA\vx+\ve) = 1  | \rank(\vS) = \alpha] - \Pr[D(\vA, \vu) =1 | \rank(\vS) = \alpha]|> \epsilon - \ngl(n).
$
\end{corollary}

@@

\subsection{Proof of \lemref{lem:i t poly time}}
\label{sec:proof lem i t poly time}
\begin{proof}
Note that $\decode_t$ will stop if $w$ and $w'$ agree on all the rows selected in Step 2 (it may also stop for other reasons---namely, in step 4; but we do not use this fact to bound the expected running time).
The probability of each selected row having an error is at most $\frac{t}{m - i}$ where $i$ is the number of rows already selected.  That is,
\begin{align*}
\Pr[i_1,..., i_{2n}\text{ have no errors}]&\geq \prod_{i=0}^{2n-1}\left(1 - \frac{t}{m-i}\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\left(\frac{m}{n}-2\right)\log n}{m-i}\right)\\
&\geq  \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\left(\frac{m-2n}{m-i}\right)\right)\geq \prod_{i=0}^{2n-1}\left( 1-\frac{d\log n}{n}\right) \\
&= \left(1-\frac{d\log n}{n}\right)^{2n}  = \left(\left(1-\frac{d\log n}{n}\right)^{\frac{n}{d\log n}}\right)^{2d\log n}\geq \frac{1}{4^{2d\log n}} = \frac{1}{n^{4d}}\,.
\end{align*}
(The second-to-last step holds as long as $n\ge 2d\log n$.) Because at each iteration, we select $2n$ rows independently at random, the expected number of iterations is at most $n^{4d}$; each iteration takes $O(n^3)$ operations in $\Fq$, which gives us the expected running time bound.

The probability that $\decode_t$ outputs $\perp$ is bounded by 
\begin{eqnarray*}
\Pr[\decode_t\rightarrow \perp]& \le & \sum_{j=1}^\infty \Pr[\decode_t\rightarrow \perp \text{ in $j$th iteration of step 4}]\\
&= &\sum_{j=1}^\infty  \Pr[\decode_t \text{ has not stopped after $j-1$ iterations} \wedge \rank(\vA_{i_1,\dots, i_{2n}})<n]\\
&\le &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times} \wedge \rank(\vA_{i_1,\dots, i_{2n}})<n]\\
&= &\sum_{j=1}^\infty  \Pr[i_1,..., i_{2n}\text{ had errors $j-1$ times}]\cdot \Pr[\rank(\vA_{i_1,\dots, i_{2n}})<n]\\
&\le &\sum_{j=1}^\infty  \left(1-\frac{1}{n^{4d}}\right)^{j-1} \cdot q^{-n}\\
& = & n^{4d} e^{-\Omega(n)} = e^{-\Omega(n)}\,.
\end{eqnarray*}
The third line from the bottom follows from the fact that the locations of the errors are assumed to be independent of the sketch, and therefore independent of the matrix $\vA$.
The second line from the bottom follows from \clref{cl:full rank matrix} when $\beta = n$; note that, because we use the union bound and evaluate the probability separately for each value of $j$,  we can treat $\vA_{i_1,\dots, i_{2n}}$ as a randomly chosen $2n\times n$ matrix, ignoring the fact that these matrices are correlated.

We claim that if the code generated by $\vA$ 
has distance at least $2t+1$, then $\decode_t$ will output $\perp$ or the correct $\vx'=\vx$.
Indeed, suppose $\vx'\neq \vx$. Since $\vA (\vx-\vx')$ has at least $2t+1$ nonzero coordinates by the minimum distance of the code generated by $\vA$, and at most  $t$ of those can be zeroed out by the addition of  $w-w'$, such an $\vx'$ will not pass Step 6.
